---
title: "Using R"
author: "Shiro Kuriwaki"
date: "`r format(Sys.time(), '%B %d, %Y')`"

output:
  html_document:
    number_sections: true
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Code and Console

```
```


# Calculators
```{r}
1 + 1
43/10
```



# Assignment
Use the left arrow to assign stuff to other stuff:
```{r}
myname <- "shiro"
```

How do you create a vector, i.e. a list of strings? Wrap it around `c(` and `)`
```{r}
myvec <- c(1, 2, 3, 4)
```


# Functions
Functions are things that take in something, manipulate them, and then output it.  It is structured like this

```{r}
print_name <- function(name) {
  
  print(paste("Hello", name))
  
}
```


```{r}
compute_average <- function(x) {
  n <- length(x)
  summed <- sum(myvec)
  mean <- summed / n
  return(mean)
}
```



# Packages
Packages are basically a set of functions that other people have written for you. They're useful because you don't have to write important functions from scratch!

Let's install Kosuke's package. You can see what it looks like on this webpage <https://github.com/kosukeimai/qss>

It tells you to first install a different package called `devtools`. Follow his command and enter this command.
```{r, eval = F}
install.packages("devtools")
```

Notice that `install.packages` is also a function

Now it tells you to run this:
```{r, eval = FALSE}
devtools::install_github("kosukeimai/qss-package", build_vignettes = TRUE)
```






# Interlude: File Structure

* A __directory__ = folder
* Your __working directory__ : the folder that you are in.
* A __parent directory__ is the folder that your current directory is in. 



Commands to move around directories (i.e., move around folders using code)

* `ls` stands for __list__ . it will show you all the files in
* `cd` stands for __change directory__. Tell your computer to go to. a certain directory.  In R, this is `setwd`
* `getwd()` in R will tell you which directory you are in.
* `~/` is an abbreviation for your Computer's default directory.
* If you want to go without abbreviation, you can type all this: `/Users/shirokuriwaki/`
* `.` is an abbreviation for current directory
* `..` is an abbreviation for the __parent directory__


Directories, as you know, are nested. Go deeper into the tree with the slash `/`
```{r eval = F}
getwd()
```


I am now going to set my working directory.

```{r, eval = FALSE}
setwd("~/Dropbox/cces_cumulative")
```


# Reading Data
You almost never hand-enter raw data on your own. So, you need to read in files into R: `.csv`, `.dta`, `.txt` .... There are functions for each of these. People have made all kinds of functions for 


`Rds` or `Rdata` is R-specific, but it's fast and error-less. 
```{r, eval = FALSE}
cces <- readRDS("data/source/person.Rds")
```


Here are some other functions 
```{r, eval = F}
read_csv
read_dta()
read_spss()
read_table()
read_excel()

```

# Visualization





