---
output:
  pdf_document:
    latex_engine: xelatex
    template: sk_helvet.sty
    keep_tex: TRUE
title: "CCES Cumulative Common Content (2006 - 2016)"
author: "Shiro Kuriwaki"
thanks: "Department of Government, Harvard University. Email: \\url{kuriwaki@g.harvard.edu}. My thanks to Alexander Agadjanian, Steve Ansolabehere, Stephen DiMauro, Bernard Fraga, Nathan Kaplan, Stephen Pettigrew, Joe Williams, and the Crunch Team for their contributions and guidance."
date: "Guide last updated: `r Sys.Date()`"
---

\renewcommand\UrlFont{\color{crimson}\ttfamily}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "")
```

```{r, include = FALSE}
library(crunch)
library(glue)
library(tidyverse)
library(haven)
library(rprojroot)

df <- readRDS(find_rstudio_root_file("data/release/cumulative_2006_2016.Rds"))
# saveRDS(sample_frac(df, 0.01), "data/release/temp_sample.Rds")
meta <- readRDS(find_rstudio_root_file("data/output/02_questions/cumulative_vartable.Rds"))
```

```{r}
print_tab <- function(var, do_sort = FALSE, tbl = df) {
  var <- enquo(var)
  
  tal <- tbl %>% 
    mutate_if(is.labelled, as_factor) %>% 
    group_by(!!var) %>% 
    tally(sort = do_sort)
  
  dframe <- as.data.frame(tal)
  
  print(dframe, row.names = FALSE)
  cat("\n\n")
}
```

```{r}
print_numeric <- function(var, tbl = df) {
  var <- enquo(var)
  
  summary(pull(df, !!var))
}
```


```{r}
in_years <- function(var, tbl = df) {
  var <- enquo(var)
  
  yrs_vec <- tbl %>% 
    filter(!is.na(!!var)) %>% 
    distinct(year) %>% 
    arrange(year) %>%
    pull() 
  
  if (identical(yrs_vec, 2006:2016)) return("All of 2006-2016")  
  if (identical(yrs_vec, 2006:2017)) return("All of 2006-2017")  
  if (!(identical(yrs_vec, 2006:2016) | identical(yrs_vec, 2006:2017))) return(str_c(yrs_vec, collapse = ", "))
}
```

```{r}
descrip <- function(var, tbl = meta) {
  varchar <- quo_name(enquo(var))
  tbl$description[tbl$alias == varchar]
}
```

```{r}
nam <- function(var, tbl = meta) {
  varchar <- quo_name(enquo(var))
  glue("`{varchar}`: {tbl$name[tbl$alias == varchar]}")
}
```

> Kuriwaki, Shiro, 2018, "Cumulative CCES Common Content (2006-2016)", \href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/II2DB6}{\url{doi:10.7910/DVN/II2DB6}}, Harvard Dataverse


\noindent This dataset combines eleven years (2006 - 2016) of the Cooperative Congressional Election Study (Principal Investigators: Stephen Ansolabehere, Brian Schaffner, and Sam Luks).

The Cooperative Congressional Election Study (CCES) is an online survey conducted around November of each year, asking a range of questions on political behavior and public opinion. While questions can change from year to year, some standard questions like the ones this cumulative file includes allow for interesting comparisons. 

This dataset was constructed based off CCES datasets from each year. A set of R scripts formatted, merged, and standardized these datasets to generate a `tibble`-style data frame. In addition, the same dataset is available on `Crunch`, an accessible analytics interface optimized for survey datasets.  

Please note that this cumulative dataset makes modifications to the original CCES datasets for comparability. These modifications are only made when differences are deemed sufficiently minor, and are documented in source code (see below). However, for details on the survey methodology and a list of all questions, readers should consult the guides for each year.  


\bigskip


\begin{tcolorbox}[boxrule=0pt,  fonttitle=\bfseries, subtitle style={boxrule=0.4pt, colback=black!75!white}]

\tcbsubtitle{To see the source code, }
report a bug, or ask a question about the data, please feel free to file an issue from the source code page:  \url{https://github.com/kuriwaki/cces_cumulative}. Alternatively, please contact me by email.

\tcbsubtitle{To obtain the individual year's CCES datasets,}
search the CCES dataverse (\url{https://dataverse.harvard.edu/dataverse/cces}) or access the CCES homepage (\url{https://cces.gov.harvard.edu/}).

\tcbsubtitle{To examine the survey methodology, }
consult the Methodology section of the most recent Common Content's codebook: \url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/GDF6Z0}.

\end{tcolorbox}

\bigskip

\newpage

# Getting Started

The `.Rds` format can be read into R. This format preserves dataset properties such as the distinction between integers and doubles, and labelled variables.
```{r, eval = FALSE, echo = TRUE}
df <- readRDS("cumulative_2006_2016.Rds")
```

The dataset in R is best viewed in `dplyr`, although it can be analyzed as a standard data frame.
```{r, echo = TRUE}
library(tidyverse)
df
```


A Stata dta file is provided as well. `cumulative_2006_2016.dta` can be read by Stata, or in R by the `haven` package 

```{r, eval = FALSE, echo = TRUE}
library(haven)
df <- read_dta("cumulative_2006_2016.dta")
```

# Features of the 2006 - 2016 Cumulative Dataset

## Unified Variable Names

Most variables in this dataset come straight from each year's CCES. However, it renames and standardizes variable names, making them accessible in one place.  Please see the rest of this guide or the Crunch dataset for a full list and description of variables. 


## Chosen Candidate Names and Identifiers
One addition to this cumulative dataset are variables of candidate names and identifiers that a respondent chose. In the individual year's CCES datasets, typically the response values for a vote choice question is a generic label, e.g. `Candidate1` and `Candidate2`. Then, separate variables of names and parties correspond to each `Candidate1` and `Candidate2`. 

Instead, the cumulative dataset shows both the generic label _and_ the chosen candidate's name, party, and identifier, which will vary across individuals. 

```{r, echo = TRUE}
select(df, year, case_id, st, matches("voted_sen"))
```


## Crunch

A version of the dataset is also included in Crunch, a database platform that makes it easy to view and analyze survey data either with our without any programming experience. Crunch is in beta at the time of writing.

1. Obtain Access: For View access to the dataset (free), please sign up here: <https://harvard.az1.qualtrics.com/jfe/form/SV_066hQi4Eeco3Kap>. For questions and more access, please contact the CCES Team.

\newpage

2. Browse: Crunch offers a web GUI for quickly browsing variables:

\begin{figure}[H]
\centering
\centerline{\includegraphics[width=1.05\linewidth]{01_crunch_browse.png}}
\end{figure}

3. Analyze: The crunch interface allows Viewers to make cross-tabs and bar graphs quickly.  
\begin{figure}[H]
\centering
\centerline{\includegraphics[width=1.05\linewidth]{02_crunch_tab.png}}
\end{figure}

Crunch datasets can also be manipulated from a R package, `crunch` <https://github.com/Crunch-io/rcrunch>. 

\newpage

# Variables

The sections below provide summary more information on each variable. 

* The title shows the name as used in the dataset, suitable for coding ("alias" in Crunch terminology). followed by a more descriptive. name suitable for presentation ("name" in Crunch terminology).
* Question wordings, where applicable, immediately follow. Otherwise an description is provide in square brackets (`[  ]`). All square brackets, both in the description and the response options, indicate descriptions that are summaries of what the respondent saw rather than the question verbatim. 
* A tabulation of response options (or summary statistics for numeric variables) follow. Numbers are unweighted counts.
* The "Years" bullet lists the years of the CCES in which data on the variable is available at all. If a year is not listed, either the question was not asked in the year or was not incorporated in the creation of this dataset. 
* Finally, the "Limitations" bullet notes some of the caveats required when interpreting this variable. As this dataset is combinations of different surveys, some year-specific details on implementation are inevitably lost. For example, for all 2016 responses "Not Asked" and "Skipped" are both coded as a `NA` (missing) to stay consistent with past years that did not make that finer distinction.

 
 
# Administration


### `r nam(year)`

`r descrip(year)`

```{r}
print_tab(year)
```

### `r nam(starttime)`

`r descrip(starttime)`

```{r}
print_numeric(starttime)
```
* Years: `r in_years(starttime)`


### `r nam(tookpost)`

`r descrip(tookpost)`

```{r}
print_tab(tookpost)
```

* Years: `r in_years(tookpost)` (Post-election wave only exists for even years)




# Weights 
### `r nam(weight)`

`r descrip(weight)`

```{r}
print_numeric(weight)
```

* Years: `r in_years(weight)`
* In even years, they are re-computed after vote validation has been computed and those re-computed weights are taken here when available. The weights applied to the sample (which is originally drawn from a matched sample) are constructed to make each year's respondents' pool representative of the national adult population. See the methodology section of the [2016 Guide](https://dataverse.harvard.edu/api/access/datafile/3047286) for details. 
* Limitations: Only specific to each year. Built off of the entire pre-election wave sample, but not necessarily to adjust post-election wave respondents. See `weight_post` 


### `r nam(weight_cumulative)`

`r descrip(weight_cumulative)`


```{r}
print_numeric(weight_cumulative)
```

* Years: `r in_years(weight_cumulative)`
* Limitations: Only a simple transformation of `weight`



### `r nam(weight_post)`

`r descrip(weight_post)`

```{r}
print_numeric(weight_post)
```

* Years: `r in_years(weight_post)`
* Limitations: Only available for some even years.



# Geography

A series of variables for the respondent's location

* `r nam(state)`: `r descrip(state)`
* `r nam(st)`: `r descrip(st)`
* `r nam(dist)`: `r descrip(dist)`
* `r nam(dist_up)`: `r descrip(dist_up)`
* `r nam(cd)`: `r descrip(cd)`
* `r nam(zipcode)`: `r descrip(zipcode)`
* `r nam(county_fips)`: `r descrip(county_fips)`

```{r}
df %>%
  mutate(is_2012 = year == 2012) %>%
  arrange(desc(is_2012)) %>%
  select(matches("(state|^st$|dist|cd|zipcode|county_fips)")) %>% 
  glimpse()
```

* Years: `r in_years(state)`
* Limitations: Some years do not provide the variable relevant to `dist_up`, in which case the current district (`dist`) is assigned automatically. Thus, `dist_up` may not reflect, for example, district changes in off-cycle redistricting.  Only residence (not registration) geographies included here; see individual years' for registration geographies.


# Demographics

### `r nam(gender)`

`r descrip(gender)`


```{r}
print_tab(gender)
```

* Years: `r in_years(gender)`

### `r nam(birthyr)`

`r descrip(birthyr)`


```{r}
print_numeric(birthyr)
```

* Years: `r in_years(birthyr)`

### `r nam(age)`

`r descrip(age)`


```{r}
print_numeric(age)
```

* Years: `r in_years(age)`

### `r nam(educ)`

`r descrip(educ)`


```{r}
print_tab(educ)
```

* Years: `r in_years(educ)`

### `r nam(race)`

`r descrip(race)`


```{r}
print_tab(race)
```

* Years: `r in_years(race)`
* Limitations: The "Hispanic" value may undercount self-identified Hispanics. See `hispanic`

### `r nam(hispanic)`

`r descrip(hispanic)`


```{r}
print_tab(hispanic)
```

* Years: `r in_years(hispanic)`
* In years  in which this question was fielded, this question supplements the `race` variable by asking does who did _not_ respnd "Hipsanic" in the `race` question.

### `r nam(faminc)`

`r descrip(faminc)`


```{r}
print_tab(faminc)
```

* Years: `r in_years(faminc)`
* Limitations: The income brackets provided in the question has changed slightly over time. The brackets in this cumulative dataset coarsens the brackets so that the bracket labeling are all correct, but with loss of some granularity. In particular, the brackets from 2006 - 2010 are different from those before. From 2011-2016, brackets over 150k were asked in a follow-up question when the respondent initially selected "over 150k". These are all grouped in this cumulative dataset.


\newpage


# Validations 

### `r nam(vv_regstatus)`

`r descrip(vv_regstatus)`

```{r}
print_tab(vv_regstatus)
```

* Years: `r in_years(vv_regstatus)`
* Limitations: Collapses some response options


### `r nam(vv_party_gen)`

`r descrip(vv_party_gen)`

```{r}
print_tab(vv_party_gen)
```

* Years: `r in_years(vv_party_gen)`
* Limitations: Not available for some even years


### `r nam(vv_party_prm)`

`r descrip(vv_party_prm)`


```{r}
print_tab(vv_party_prm)
```

* Years: `r in_years(vv_party_prm)`
* Limitations: Not available for some even years

## Turnout 

### `r nam(vv_turnout_gvm)`

`r descrip(vv_turnout_gvm)`


```{r}
print_tab(vv_turnout_gvm)
```

* Years: `r in_years(vv_turnout_gvm)`
* Limitations: Collapses most response options. In particular, the particular voting method is collapsed into one category, even though `gvm` stands for General Election voting method. Also, the result of not matching to a voter file is collapsed with the result of matching to a voter file and having no indication of turning out to vote. The distinction is unclear in earlier years, and is thus collapsed for all years here. For finer distinctions, see the individual year's CCES.

### `r nam(vv_turnout_pvm)`

`r descrip(vv_turnout_pvm)`


```{r}
print_tab(vv_turnout_pvm)
```

* Years: `r in_years(vv_turnout_pvm)`
* Limitations: See `vv_turnout_gvm`

\newpage

# Identity and Attitudes

## Partisan Identity

### `r nam(pid3)`

`r descrip(pid3)`

```{r}
print_tab(pid3)
```

* Years: `r in_years(pid3)`
* Limitations: Response options offer slightly by year. For example, the `Not Sure` option is not a response option in years 2006 and 2010.  Open-text responses not included. 2010 values are from the post-election wave. 


### `r nam(pid7)`

`r descrip(pid7)`

```{r}
print_tab(pid7)
```

* Years: `r in_years(pid7)`
* Limitations: See `pid3` 

### `r nam(pid3_leaner)`

`r descrip(pid3_leaner)`

```{r}
print_tab(pid3_leaner)
```

* Years: `r in_years(pid3_leaner)`
* Limitations: See `pid3`


## Economy
### `r nam(economy_retro)`

`r descrip(economy_retro)`

```{r}
print_tab(economy_retro)
```

* Years: `r in_years(economy_retro)`
* Limitations: Response options varies by year. Some are collapsed into one category (e.g. `Gotten Better`, presented in some years, and `Gotten Somewhat Better`, presented in other years, are collapsed into `Gotten Better / Somewhat Better`). Some are left as is. For example, `Not Sure` was not an option in 2009.


## Approval

### `r nam(approval_pres)`

`r descrip(approval_pres)`


```{r}
print_tab(approval_pres)
```

* Years: `r in_years(approval_pres)`
* Limitations: `Neither approve nor disapprove` only included in 2007.
* This question is asked in a grid format, along with Governors, Congress, and Courts. 

### `r nam(approval_rep)`

`r descrip(approval_rep)`


```{r}
print_tab(approval_rep)
```

* Years: `r in_years(approval_rep)`
* Limitations: `Neither approve nor disapprove` only included in 2007.
* This question is asked in a grid format, along with Senators (`approval_sen1`, `approval_sen2`). 
* To see who [Representative] refers to for a particular respondent, see `rep_inc` (incumbent identifier in `rep_icpsr`)

### `r nam(approval_sen1)`

`r descrip(approval_sen1)`


```{r}
print_tab(approval_sen1)
```

* Years: `r in_years(approval_sen1)`
* Limitations: : Response options varies by year. Some are collapsed into one category (e.g. `Approve`, presented in some years, and `Somewhat Approve`, presented in other years, are collapsed into `Approve / Somewhat Approve`). `Neither approve nor disapprove` only included in 2007.
* To see who [Senator 1] refers to for a particular respondent, see `sen1_inc` (incumbent identifier in `sen1_icpsr`)

### `r nam(approval_sen2)`

`r descrip(approval_sen2)`


```{r}
print_tab(approval_sen2)
```

* See `approval_sen2`

### `r nam(approval_gov)`

`r descrip(approval_gov)`


```{r}
print_tab(approval_gov)
```

* Years: `r in_years(approval_gov)`
* Limitations: See `approval_pres`
* To see who the Governor refers to for a particular respondent, see `gov_inc` (incumbent identifier in `gov_fec`, if applicable).



\newpage

# Presidential Vote

\begin{tcolorbox}[title={A note on \texttt{intent} and \texttt{voted}}]
In this dataset we make the distinction between "intent" / "preference" vs. "voted" / "vote choice". "Intent" (or "preference") refers to the response to the prospective question of the sort "who would you vote for?" in the \emph{pre-election} wave. "Vote choice" refers to the response to the retrospective question of the sort "in the election this November, who did you vote for?" Response to the vote choice questions coalesces both \emph{post-election} wave responses (the bulk of the responses) and pre-election respondents who reported having already voted early. 
\end{tcolorbox}


### `r nam(intent_pres_08)`

`r descrip(intent_pres_08)`


```{r}
print_tab(intent_pres_08)
```

* Years: `r in_years(intent_pres_08)`


### `r nam(intent_pres_12)`

`r descrip(intent_pres_12)`


```{r}
print_tab(intent_pres_12)
```

* Years: `r in_years(intent_pres_12)`

### `r nam(intent_pres_16)`

`r descrip(intent_pres_16)`


```{r}
print_tab(intent_pres_16)
```

* Years: `r in_years(intent_pres_16)`


### `r nam(voted_pres_08)`

`r descrip(voted_pres_08)`


```{r}
print_tab(voted_pres_08)
```

* Years: `r in_years(voted_pres_08)`
* Limitations: Response options offer slightly by year; some are collapsed into one. 

### `r nam(voted_pres_12)`

`r descrip(voted_pres_12)`

```{r}
print_tab(voted_pres_12)
```

* Years: `r in_years(voted_pres_12)`
* Limitations: Response options offer slightly by year; some are collapsed into one. 
* This variable coalesces two variables: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.

### `r nam(voted_pres_16)`

`r descrip(voted_pres_16)`

```{r}
print_tab(voted_pres_16)
```

* Years: `r in_years(voted_pres_16)`
* This variable coalesces two variables in the CCES: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.


# House, Senate and Governor Voting

## Preference

### `r nam(intent_rep)`

`r descrip(intent_rep)`


```{r}
print_tab(intent_rep)
```

* Years: `r in_years(intent_rep)`
* Limitations: Only available for even years. The third party candidate not specified for early years. The fourth candidate and onwards not shown for most years.  Response options differ by year.
* Note that for each respondent, a name (and party affiliation) is shown in place of the square bracket values. To see the candidate chosen, see `intent_rep_chosen`. `[Other / Candidate 3]` refers to the third option presented, whereas `Other` refers to the unnamed choice after all numbered candidates. 



### `r nam(intent_sen)`

`r descrip(intent_sen)`

```{r}
print_tab(intent_sen)
```

* Years: `r in_years(intent_sen)`
* Limitations: See `intente_rep`. When both senate seats are up for re-election in the same year, only responses to the first senate seat is incorporated. For the second senate seat, see individual year's CCES.

### `r nam(intent_gov)`

`r descrip(intent_gov)`


```{r}
print_tab(intent_gov)
```

* Years: `r in_years(intent_gov)`
* Limitations: See `intente_rep`. For governor elections in odd years, see individual year's CCES.


## Vote Choice

### `r nam(voted_rep)`

`r descrip(voted_rep)`

```{r}
print_tab(voted_rep)
```

* Years: `r in_years(voted_rep)`
* This variable coalesces two variables in the CCES for years 2012 and onwards: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.

### `r nam(voted_sen)`

`r descrip(voted_sen)`


```{r}
print_tab(voted_sen)
```

* Years: `r in_years(voted_sen)`
* This variable coalesces two variables in the CCES for years 2012 and onwards: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.

### `r nam(voted_gov)`

`r descrip(voted_gov)`

```{r}
print_tab(voted_gov)
```

* Years: `r in_years(voted_gov)`
* This variable coalesces two variables in the CCES for years 2012 and onwards: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.



\newpage


# Text


## Identifiers

The case identifier `case_id` is unique within the year and is identical to the case identifiers in the individual year's CCES. It should be used in conjunction with `year` for a unique identifier for the whole dataset. Some individuals across years may be the same YouGov panel respondent with different identifiers; for example the 2007 CCES draws from the 2006 CCES respondents.  

```{r}
glimpse(select(df, matches("year|case_id")))
```

## Current Representatives

### Name and Party

The four names in the three offices that represent the respondent _at the time of the survey_. Parties are not shown if the particular year's CCES did not show party. Party names are also abbreviated down to initials (`D` for Democrat, `R` for Republican, `I` for Independent) in this dataset.

```{r}
glimpse(select(df, matches("(rep|sen1|sen2|gov)_current")))
```

### Incumbent Identifiers

Unique identifiers (ICPSR / Nominate for Congress, FEC for Governor) for the current representatives. Identifiers are not part of the individual year's CCES but merged on for this cumulative dataset only. 

The matching of identifiers to respondent occurs through matching by district, by district and last name, or both:

* For House representatives, we join on `cong`, `st`, and  `dist` to a NOMINATE database that only consists of unique observations according to the key. For duplicates with regards to these three variables (e.g. in the rare case where a new representative comes into office mid-session), we match on `cong`, `st`, `dist` and last name.
* For Senators, we join entirely on `cong`, `st`, and last name
* For Governors, we join only on `st` and last name. In this period, there are no two governors in the same state that share the same last name. 


```{r}
glimpse(select(df, matches("(rep|sen1|sen2|gov)_.*icpsr"), gov_fec))
```

* Years: `r in_years(rep_icpsr)`
* Limitations: Matching procedure may be incomplete or inaccurate.

The unique identifiers can be used to join with other databases to append additional information such as committee membership and ideology scores, such as 

> Lewis, Jeffrey B., Keith Poole, Howard Rosenthal, Adam Boche, Aaron Rudkin, and Luke Sonnet (2017). Voteview: Congressional Roll-Call Votes Database. <https://voteview.com/>

## Candidates

The text responses that the respondent chose in each of the `intent_` / `voted_` questions, if the respondent was a candidate. For example, respondent with `case_id = 163051575` in the 2012 CCES chose the first option in the House representative preference question. `intent_rep_chosen` shows that for this particular respondent, the first option was `Maxine Waters (Democrat)` who has a FEC Identifier of `H4CA23011`.

```{r, echo = TRUE}
df %>% 
  filter(year == 2012, st == "CA", dist_up == 43) %>% 
  select(matches("intent_rep")) 
```

The name and party are those as provided in the CCES datasets (e.g. in the form `HouseCand1Name`). The FEC ID is not part of the CCES but joined in this dataset. 

For all three offices, the matching generally occurs by `year`, `st`, `dist_up` (not `dist`, because `dist_up`, refers to the district of the upcoming session) and `party`.  `party` is the party affiliation as indicated in the CCES. For years 2008 and 2010, the first option is automatically labelled as a Democrat and the second option as a Republican, although these may be inaccurate at times. 

The FEC database originates from

> Bonica, Adam , 2015, "Database on Ideology, Money in Politics, and Elections (DIME)", <doi:10.7910/DVN/O5PX0B>, Harvard Dataverse, V2


which helpfully includes candidates office sought, district (for House members), party affiliation, and cycle in which the candidate filed. The variable `cycle` in Bonica's data is used to join on the CCES dataset's `year` variable. 

Only candidates who are unique within the district and party are considered for the first join. However, many candidates are not unique within the district-party, as many co-partisans may file in the same district. The second matching process thus considers the full name of the candidate listed in the CCES and the candidates in the FEC database. _Within_ the subset of year, district, and party, a Jaro-Winker string distance (that ranges from 0 to 1) is computed for both last name and the first name - middle name. If the sum of the two string distances are more than 0.2 for all possible combinations, no match is returned. If there is a unique combination that achieves a unique minimum that is below 0.2, that combination is declared a match. If there are multiple matches with the same minimum string distance, one is randomly chosen. 


### Chosen
```{r}
glimpse(select(df, matches("(intent|voted)_.*chosen")))
```

* Years: `r in_years(intent_rep_chosen)`
* Early years may mislabel the candidate's party, especially when the two candidates are of the same party (as in top-two primary states)

### Candidate Identifiers
```{r}
glimpse(select(df, matches("(intent|voted)_.*fec")))
```

* Years: `r in_years(intent_rep_fec)`
* Limitations: Matching may be inaccurate (see previous section on matching methodology). In particular, a lack of a FEC ID may either indicate a failure of the matching procedure, or that the candidate in question did not file under the FEC.  The match rate in the current procedure is upwards of 80 percent in the current procedure. 