---
output:
  pdf_document:
    latex_engine: xelatex
    template: sk_helvet.sty
title: "CCES Cumulative Common Content (2006 - 2016)"
author: "Shiro Kuriwaki"
thanks: "Department of Government, Harvard University. \url{www.shirokuriwaki.com}. Thanks to Steve Ansolabehere, Stephen DiMauro, Nathan Kaplan, Stephen Pettigrew, Joe Williams, and the Crunch Team for datasets, code, and guidance."
date: "Codebook Last Updated: `r Sys.Date()`"
urlcolor: MidNightBlue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "")
```

```{r, include = FALSE}
library(crunch)
library(glue)
library(tidyverse)
library(haven)
library(rprojroot)
```
```{r include = FALSE}
df <- readRDS(find_rstudio_root_file("data/release/cumulative_2006_2016.Rds"))
# saveRDS(sample_frac(df, 0.01), "data/release/temp_sample.Rds")
meta <- readRDS(find_rstudio_root_file("data/output/02_questions/cumulative_vartable.Rds"))
```

```{r}
print_tab <- function(var, do_sort = FALSE, tbl = df) {
  var <- enquo(var)
  
  tal <- tbl %>% 
    mutate_if(is.labelled, as_factor) %>% 
    group_by(!!var) %>% 
    tally(sort = do_sort)
  
  dframe <- as.data.frame(tal)
  
  print(dframe, row.names = FALSE)
  cat("\n\n")
}
```

```{r}
print_numeric <- function(var, tbl = df) {
  var <- enquo(var)
  
  summary(pull(df, !!var))
}
```


```{r}
in_years <- function(var, tbl = df) {
  var <- enquo(var)
  
  yrs_vec <- tbl %>% 
    filter(!is.na(!!var)) %>% 
    distinct(year) %>% 
    arrange(year) %>%
    pull() 
  
  if (identical(yrs_vec, as.numeric(2006:2016))) return("All of 2006-2016")  
  if (!identical(yrs_vec, as.numeric(2006:2016))) return(str_c(yrs_vec, collapse = ", "))
}
```

```{r}
descrip <- function(var, tbl = meta) {
  varchar <- quo_name(enquo(var))
  tbl$description[tbl$alias == varchar]
}
```

```{r}
nam <- function(var, tbl = meta) {
  varchar <- quo_name(enquo(var))
  glue("`{varchar}`: {tbl$name[tbl$alias == varchar]}")
}
```

This dataset combines responses from eleven years (2006 - 2016) of the Cooperative Congressional Election Study (CCES, Principal Investigators: Stephen Ansolabehere, Brian Schaffner, and Sam Luks). 

The CCES is an online survey conducted around November of each year, asking a wide range of questions on political behavior and public opinion. One particular strength of the CCES is its relatively large sample size that covers all Congressional districts. While questions can change from year to year, some standard questions, as this compiled file contains, afford comparison. 

The dataset was constructed based off the public flat file CCES datasets from each year. A set of R scripts formatted, merged, and standardized these datasets to generate a `tibble`-style data frame in `R`. A `Stata` `.dta` file is also provided, generated from the `haven` package. In addition, the same data frame is uploaded to a `Crunch` interface, a new online tool (in beta at the time of writing) that makes data visualization and tabulation intuitive and sharable.  

This dataset sometimes standardizes responses whose question wording or response options that have changed slightly over years. These modifications are only made when differences are deemed sufficiently minor, and are documented in source code (see below). However, for details on the survey methodology and a list of all questions, readers should consult the guides for each year.  

# Links

* For source code that created this dataset's variables and formatting, see the Github repository \url{https://github.com/kuriwaki/cces_cumulative}
* To report a bug in the dataset or ask a question about the build process, please feel free to file an issue at the same page, \url{https://github.com/kuriwaki/cces_cumulative/issues}. Alternatively, please contact me by email: \url{kuriwaki@g.harvard.edu}
* The CCES homepage is \url{https://cces.gov.harvard.edu/}
* For each year's CCES datasets and more, search the CCES dataverse: \url{https://dataverse.harvard.edu/dataverse/cces}
* A cumulative file for 2006-2012, in a slightly different format, is:  Ansolabehere, Stephen; Pettigrew, Stephen, 2014, ["Cumulative CCES Common Content (2006-2012)"](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/26451), \url{doi:10.7910/DVN/26451}, Harvard Dataverse, V5, UNF:\texttt{5:rXSA73aoDi28uu+IOg7DEg==}
* To read more on the survey methodology, consult the Methodology section of the most recent Common Content's codebook: Ansolabehere, Stephen; Schaffner, Brian F., 2017, "CCES Common Content, 2016", \url{doi:10.7910/DVN/GDF6Z0}, Harvard Dataverse, V3, UNF:\texttt{6:Hacct7qJt1WXOGPb63A5Gg==}


# Getting Started

The `.Rds` format can be read into R. This format preserves dataset properties such as the distinction between integers and doubles, and labelled variables.
```{r, eval = FALSE, echo = TRUE}
df <- readRDS("cumulative_2006_2016.Rds")
```

The dataset in R is best viewed in `dplyr`, although it can be analyzed as a standard data frame.
```{r, echo = TRUE}
library(tidyverse)
df
```


A Stata dta file is provided as well. `cumulative_2006_2016.dta` can be read by Stata, or in R by the `haven` package 

```{r, eval = FALSE, echo = TRUE}
library(haven)
df <- read_dta("cumulative_2006_2016.dta")
```

# Features

## Unified Variable Names

## Candidate Names and Identifiers
One addition to this cumulative dataset above the individual years that comprise it is the addition of candidate name and identifiers that a respondent chose. In the individual year's CCES datasets, typically the response values for a vote choice question is a generic label, e.g. `Candidate1` and `Candidate2`. Then, separate variables with those names are appended, requiring users to look-up the relevant candidate for each respondent. The cumulative dataset shows both the generic label _and_ the chosen candidate's name, party, and identifier, which will vary across individuals. 

```{r, echo = TRUE}
select(df, year, case_id, st, matches("voted_sen"))
```

## Crunch

1. Obtain Access

2. Browse

3. Analyze: The crunch interface allows Viewers to make 






# Variables

The sections below provide summary more information on each variable. 

* The title is followed by the name of the variable in the dataset ("alias" in Crunch) followed by the variable label ("name" in Crunch).
* Question wordings, where applicable, immediately follow. Otherwise an description is provide in square brackets ("[]"). All square brackets, both in the description and the response options, indicate descriptions that are summaries of what the respondent saw (rather than the verbatim response). 
* A tabulation of response options (or summary statistics for numeric variables) follow. Numbers are unweighted counts. Options are ordered by the ordering of the options. 
* The "Years" variable lists the years of the CCES in which data on the variable is available at all. If a year is not listed, either the question was not asked in the year or was not incorporate in the creation of this dataset. 
* Finally, "Limitations" notes some of the caveats required when interpreting this variable. As this dataset is synthetic, some year-specific details on implementation are inevitably lost.
 
 
 
# Administration


### `r nam(year)`

`r descrip(year)`

```{r}
print_tab(year)
```

### `r nam(starttime)`

`r descrip(starttime)`

```{r}
print_numeric(starttime)
```
* Years: `r in_years(starttime)`


### `r nam(tookpost)`

`r descrip(tookpost)`

```{r}
print_tab(tookpost)
```

* Years: `r in_years(tookpost)` (Post-election wave only exists for even years)




# Weights 
### `r nam(weight)`

`r descrip(weight)`

```{r}
print_numeric(weight)
```

* Years: `r in_years(weight)`
* The weights applied to the sample (which is originally drawn from a matched sample) are constructed to make each year's respondents' pool representative of the national adult population. See the methodology section of the [2016 Guide](https://dataverse.harvard.edu/api/access/datafile/3047286) for details. 
* Limitations: Only specific to each year. Built off of the entire pre-election wave sample, but not necessarily to adjust post-election wave respondents. 


### `r nam(weight_cumulative)`

`r descrip(weight_cumulative)`


```{r}
print_numeric(weight_cumulative)
```

* Years: `r in_years(weight_cumulative)`
* Limitations: Only a simple transformation of `weight`



### `r nam(weight_vv)`

`r descrip(weight_vv)`


```{r}
print_numeric(weight_vv)
```

* Years: `r in_years(weight_vv)`
* Limitations: Only available for some even years.

### `r nam(weight_vv_post)`

`r descrip(weight_vv_post)`

```{r}
print_numeric(weight_vv_post)
```

* Years: `r in_years(weight_vv_post)`
* Limitations: Only available for some even years.



# Geography

A series of variables for the respondent's location

* `r nam(state)`: `r descrip(state)`
* `r nam(st)`: `r descrip(st)`
* `r nam(dist)`: `r descrip(dist)`
* `r nam(dist_up)`: `r descrip(dist_up)`
* `r nam(CD)`: `r descrip(CD)`
* `r nam(zipcode)`: `r descrip(zipcode)`
* `r nam(countyFIPS)`: `r descrip(countyFIPS)`

```{r}
df %>%
  mutate(is_2012 = year == 2012) %>%
  arrange(desc(is_2012)) %>%
  select(matches("(state|^st$|dist|CD|zipcode|countyFIPS)")) %>% 
  glimpse()
```

* Years: `r in_years(state)`
* Limitations: Some years do not provide the variable relevant to `dist_up`, in which case the current district (`dist`) is assigned automatically. Thus, `dist_up` may not reflect, for example, district changes in off-cycle redistricting.  Only residence (not registration) geographies included here; see individual years' for registration geographies.


# Demographics

### `r nam(gender)`

`r descrip(gender)`


```{r}
print_tab(gender)
```

* Years: `r in_years(gender)`

### `r nam(birthyr)`

`r descrip(birthyr)`


```{r}
print_numeric(birthyr)
```

* Years: `r in_years(birthyr)`

### `r nam(age)`

`r descrip(age)`


```{r}
print_numeric(age)
```

* Years: `r in_years(age)`

### `r nam(educ)`

`r descrip(educ)`


```{r}
print_tab(educ)
```

* Years: `r in_years(educ)`

### `r nam(race)`

`r descrip(race)`


```{r}
print_tab(race)
```

* Years: `r in_years(race)`


# Presidential Vote

### `r nam(intent_pres_08)`

`r descrip(intent_pres_08)`


```{r}
print_tab(intent_pres_08)
```

* Years: `r in_years(intent_pres_08)`


### `r nam(intent_pres_12)`

`r descrip(intent_pres_12)`


```{r}
print_tab(intent_pres_12)
```

* Years: `r in_years(intent_pres_12)`

### `r nam(intent_pres_16)`

`r descrip(intent_pres_16)`


```{r}
print_tab(intent_pres_16)
```

* Years: `r in_years(intent_pres_16)`


### `r nam(voted_pres_08)`

`r descrip(voted_pres_08)`


```{r}
print_tab(voted_pres_08)
```

* Years: `r in_years(voted_pres_08)`
* Limitations: Response options offer slightly by year; some are collapsed into one. 

### `r nam(voted_pres_12)`

`r descrip(voted_pres_12)`

```{r}
print_tab(voted_pres_12)
```

* Years: `r in_years(voted_pres_12)`
* Limitations: Response options offer slightly by year; some are collapsed into one. 
* This variable coalesces two variables: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.

### `r nam(voted_pres_16)`

`r descrip(voted_pres_16)`

```{r}
print_tab(voted_pres_16)
```

* Years: `r in_years(voted_pres_16)`
* This variable coalesces two variables in the CCES: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.


# Voting

## Preference

### `r nam(intent_rep)`

`r descrip(intent_rep)`


```{r}
print_tab(intent_rep)
```

* Years: `r in_years(intent_rep)`
* Limitations: Only available for even years. The third party candidate not specified for early years. The fourth candidate and onwards not shown for most years.  Response options differ by year.
* Note that for each respondent, a name (and party affiliation) is shown in place of the square bracket values. To see the candidate chosen, see `intent_rep_chosen`. `[Other / Candidate 3]` refers to the third option presented, whereas `Other` refers to the unnamed choice after all numbered candidates. 



### `r nam(intent_sen)`

`r descrip(intent_sen)`

```{r}
print_tab(intent_sen)
```

* Years: `r in_years(intent_sen)`
* Limitations: See `intente_rep`. When both senate seats are up for re-election in the same year, only responses to the first senate seat is incorporated. For the second senate seat, see individual year's CCES.

### `r nam(intent_gov)`

`r descrip(intent_gov)`


```{r}
print_tab(intent_gov)
```

* Years: `r in_years(intent_gov)`
* Limitations: See `intente_rep`. For governor elections in odd years, see individual year's CCES.


## Vote Choice

### `r nam(voted_rep)`

`r descrip(voted_rep)`

```{r}
print_tab(voted_rep)
```

* Years: `r in_years(voted_rep)`
* This variable coalesces two variables in the CCES for years 2012 and onwards: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.

### `r nam(voted_sen)`

`r descrip(voted_sen)`


```{r}
print_tab(voted_sen)
```

* Years: `r in_years(voted_sen)`
* This variable coalesces two variables in the CCES for years 2012 and onwards: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.

### `r nam(voted_gov)`

`r descrip(voted_gov)`

```{r}
print_tab(voted_gov)
```

* Years: `r in_years(voted_gov)`
* This variable coalesces two variables in the CCES for years 2012 and onwards: Either the response to the early vote question in the pre-election wave if the respondent indicates they have already voted, or if not, the response in the post-election wave.



# Validations 

### `r nam(vv_regstatus)`

`r descrip(vv_regstatus)`

```{r}
print_tab(vv_regstatus)
```

* Years: `r in_years(vv_regstatus)`
* Limitations: Collapses some response options


### `r nam(vv_party_gen)`

`r descrip(vv_party_gen)`

```{r}
print_tab(vv_party_gen)
```

* Years: `r in_years(vv_party_gen)`
* Limitations: Not available for some even years


### `r nam(vv_party_prm)`

`r descrip(vv_party_prm)`


```{r}
print_tab(vv_party_prm)
```

* Years: `r in_years(vv_party_prm)`
* Limitations: Not available for some even years

## Turnout 

### `r nam(vv_turnout_gvm)`

`r descrip(vv_turnout_gvm)`


```{r}
print_tab(vv_turnout_gvm)
```

* Years: `r in_years(vv_turnout_gvm)`
* Limitations: Collapses most response options. In particular, the particular voting method is collapsed into one category, even though `gvm` stands for General Election voting method. Also, the result of not matching to a voter file is collapsed with the result of matching to a voter file and having no indication of turning out to vote. The distinction is unclear in earlier years, and is thus collapsed for all years here. For finer distinctions, see the individual year's CCES.

### `r nam(vv_turnout_pvm)`

`r descrip(vv_turnout_pvm)`


```{r}
print_tab(vv_turnout_pvm)
```

* Years: `r in_years(vv_turnout_pvm)`
* Limitations: See `vv_turnout_gvm`


# Identity and Attitudes

## Partisan Identity

### `r nam(pid3)`

`r descrip(pid3)`

```{r}
print_tab(pid3)
```

* Years: `r in_years(pid3)`
* Limitations: Response options offer slightly by year. For example, the `Not Sure` option is not a response option in years 2006 and 2010.  Open-text responses not included. 

### `r nam(pid7)`

`r descrip(pid7)`

```{r}
print_tab(pid7)
```

* Years: `r in_years(pid7)`
* Limitations: See `pid3` 

## Economy
### `r nam(economy_retro)`

`r descrip(economy_retro)`

```{r}
print_tab(economy_retro)
```

* Years: `r in_years(economy_retro)`
* Limitations: Response options varies by year. Some are collapsed into one category (e.g. `Gotten Better`, presented in some years, and `Gotten Somewhat Better`, presented in other years, are collapsed into `Gotten Better / Somewhat Better`). Some are left as is. For example, `Not Sure` was not an option in 2009.


## Approval

### `r nam(approval_pres)`

`r descrip(approval_pres)`


```{r}
print_tab(approval_pres)
```

* Years: `r in_years(approval_pres)`
* Limitations: `Neither approve nor disapprove` only included in 2007.
* This question is asked in a grid format, along with Governors, Congress, and Courts. 

### `r nam(approval_rep)`

`r descrip(approval_rep)`


```{r}
print_tab(approval_rep)
```

* Years: `r in_years(approval_rep)`
* Limitations: `Neither approve nor disapprove` only included in 2007.
* This question is asked in a grid format, along with Senators (`approval_sen1`, `approval_sen2`). 
* To see who [Representative] refers to for a particular respondent, see `rep_inc` (incumbent identifier in `rep_icpsr`)

### `r nam(approval_sen1)`

`r descrip(approval_sen1)`


```{r}
print_tab(approval_sen1)
```

* Years: `r in_years(approval_sen1)`
* Limitations: : Response options varies by year. Some are collapsed into one category (e.g. `Approve`, presented in some years, and `Somewhat Approve`, presented in other years, are collapsed into `Approve / Somewhat Approve`). `Neither approve nor disapprove` only included in 2007.
* To see who [Senator 1] refers to for a particular respondent, see `sen1_inc` (incumbent identifier in `sen1_icpsr`)

### `r nam(approval_sen2)`

`r descrip(approval_sen2)`


```{r}
print_tab(approval_sen2)
```

* See `approval_sen2`

### `r nam(approval_gov)`

`r descrip(approval_gov)`


```{r}
print_tab(approval_gov)
```

* Years: `r in_years(approval_gov)`
* Limitations: See `approval_pres`
* To see who the Governor refers to for a particular respondent, see `gov_inc` (incumbent identifier in `gov_fec`, if applicable).




# Text


## Identifiers

The case identifier `case_id` is unique within the year and is identical to the case identifiers in the individual year's CCES. It should be used in conjunction with `year` for a unique identifier for the whole dataset. Some individuals across years may be the same YouGov panel respondent with different identifiers; for example the 2007 CCES draws from the 2006 CCES respondents.  

```{r}
glimpse(select(df, matches("year|case_id")))
```

## Current Representatives

### Incumbents

The four names in the three offices that represent the respondent _at the time of the survey_. Parties are not shown if the particular year's CCES did not show party. 

```{r}
glimpse(select(df, matches("(rep|sen1|sen2|gov)_.inc")))
```

### Incumbent Identifiers

Unique identifiers (ICPSR / Nominate for Congress, FEC for Governor) for the current representatives. Identifiers are not part of the individual year's CCES but merged on for this cumulative dataset only. 

The matching of identifiers to respondent occurs through matching by district, by district and last name, or both:

* For House representatives, we join on `cong`, `st`, and  `dist` to a NOMINATE database that only consists of unique observations according to the key. For duplicates with regards to these three variables (e.g. in the rare case where a new representative comes into office mid-session), we match on `cong`, `st`, `dist` and last name.
* For Senators, we join entirely on `cong`, `st`, and last name
* For Governors, we join only on `st` and last name. In this period, there are no two governors in the same state that share the same last name. 


```{r}
glimpse(select(df, matches("(rep|sen1|sen2|gov)_.*icpsr"), gov_fec))
```

* Years: `r in_years(rep_icpsr)`
* Limitations: Matching procedure may be incomplete or inaccurate.

The unique identifiers can be used to join with other databases to append additional information such as committee membership and ideology scores, such as 

> Lewis, Jeffrey B., Keith Poole, Howard Rosenthal, Adam Boche, Aaron Rudkin, and Luke Sonnet (2017). Voteview: Congressional Roll-Call Votes Database. <https://voteview.com/>

## Candidates

The text responses that the respondent chose in each of the `intent_` / `voted_` questions, if the respondent was a candidate. For example, respondent with `case_id = 163051575` in the 2012 CCES chose the first option in the House representative preference question. `intent_rep_chosen` shows that for this particular respondent, the first option was `Maxine Waters (Democrat)` who has a FEC Identifier of `H4CA23011`.

```{r, echo = TRUE}
df %>% 
  filter(year == 2012, st == "CA", dist_up == 43) %>% 
  select(matches("intent_rep")) 
```

The name and party are those as provided in the CCES datasets (e.g. in the form `HouseCand1Name`). The FEC ID is not part of the CCES but joined in this dataset. 

For all three offices, the matching generally occurs by `year`, `st`, `dist_up` (not `dist`, because `dist_up`, refers to the district of the upcoming session) and `party`.  `party` is the party affiliation as indicated in the CCES. For years 2008 and 2010, the first option is automatically labelled as a Democrat and the second option as a Republican, although these may be inaccurate at times. 

The FEC database originates from

> Bonica, Adam , 2015, "Database on Ideology, Money in Politics, and Elections (DIME)", <doi:10.7910/DVN/O5PX0B>, Harvard Dataverse, V2


which helpfully includes candidates office sought, district (for House members), party affiliation, and cycle in which the candidate filed. The variable `cycle` in Bonica's data is used to join on the CCES dataset's `year` variable. 

Only candidates who are unique within the district and party are considered for the first join. However, many candidates are not unique within the district-party, as many co-partisans may file in the same district. The second matching process thus considers the full name of the candidate listed in the CCES and the candidates in the FEC database. _Within_ the subset of year, district, and party, a Jaro-Winker string distance (that ranges from 0 to 1) is computed for both last name and the first name - middle name. If the sum of the two string distances are more than 0.2 for all possible combinations, no match is returned. If there is a unique combination that achieves a unique minimum that is below 0.2, that combination is declared a match. If there are multiple matches with the same minimum string distance, one is randomly chosen. 


### Chosen
```{r}
glimpse(select(df, matches("(intent|voted)_.*chosen")))
```

* Years: `r in_years(intent_rep_chosen)`
* Early years may mislabel the candidate's party, especially when the two candidates are of the same party (as in top-two primary states)

### Candidate Identifiers
```{r}
glimpse(select(df, matches("(intent|voted)_.*fec")))
```

* Years: `r in_years(intent_rep_fec)`
* Limitations: Matching may be inaccurate (see previous section on matching methodology). In particular, a lack of a FEC ID may either indicate a failure of the matching procedure, or that the candidate in question did not file under the FEC.  The match rate in the current procedure is upwards of 80 percent in the current procedure. 